Towards atomistic resolution structure of phosphatidylcholine headgroup and glycerol backbone at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-05-15 HGmodelMANUSCRIPT/coverLETTER.tex
Final version of cover letter

Please find attached to this message a manuscript entitled `Towards atomistic resolution structure of phosphatidylcholine 
glycerol backbone and choline headgroup at different ambient conditions' by A. Botan et al., which we would like to submit 
for consideration of publication in \textit{Journal of the American Chemical Society} (JACS). In the manuscript a large amount of
existing experimental Nuclear Magnetic Resonance (NMR) data is reviewed and combined with an exceptionally comprehensive 
collection of generated molecular dynamics (MD) simulation data in order to understand the atomistic resolution structure 
of biologically abundant phospholipid molecules and their assemblies.

We believe that the manuscript is interesting to the wide and diverse contemporary audience of
JACS as it demonstrates how the combination of experimental NMR data with MD simulations is shown 
to be successful in resolving the atomistic resolution structure of biomolecules in various biologically 
relevant conditions. The approach is demonstrated for lipids, however, the extension to, e.g. membrane 
proteins is straightforward. Such an atomistic resolution of biomolecular structure significantly advances 
the understanding in fundamental chemistry, molecular biology, and also supports the development of applications, 
for example new biomaterials or drug delivery systems.

In addition to its main message, the manuscript also provides an extensive comparison on the structural quality 
of the numerous widely used computational lipid models. Therefore the manuscript provides crucial information 
for a large group scientists who are producing or reading the literature involving computational lipid models.

@@

The usage of molecular dynamics simulations and open collaboration are adequate for the
problem at hand. Indeed, such simulations are currently the most straightforward method to 
construct atomistic resolution structures to interpret NMR experiments, but
enormous amount of simulation work was required for this work. The only practical
solution to collect this data was the open collaboration concept.
As result, we have produced original chemical insight for the atomistic resolution 
structures of phospholipids in various biologically relevant conditions.

>>>>

Please find attached to this message a manuscript entitled `Towards atomistic resolution structure of phosphatidylcholine 
glycerol backbone and choline headgroup at different ambient conditions' by A. Botan et al., which we would like to submit 
for consideration of publication in \textit{Journal of the American Chemical Society} (JACS). In the manuscript a large amount of
existing experimental Nuclear Magnetic Resonance (NMR) data is reviewed and combined with an exceptionally comprehensive 
collection of molecular dynamics (MD) simulation data in order to understand the atomistic resolution structure 
of biologically abundant phospholipid molecules and their assemblies.

We believe that the manuscript is interesting to the wide and diverse contemporary audience of
JACS as it demonstrates how the combination of experimental NMR data with MD simulations can 
be successful in resolving the atomistic resolution structure of biomolecules in various biologically 
relevant conditions. The approach is demonstrated for lipids, however, the extension to, e.g., membrane 
proteins is straightforward. Such an atomistic resolution of biomolecular structure significantly advances 
the understanding in fundamental chemistry, molecular biology, and also supports the development of applications, 
for example new biomaterials or drug delivery systems.

In addition to its main message, the manuscript also provides an extensive comparison on the structural quality 
of the numerous widely used computational lipid models. This is crucial information 
for the large group scientists who are producing or reading the literature involving computational lipid models.

@@

The usage of molecular dynamics simulations and open collaboration are adequate for the
problem at hand. Indeed, such simulations are currently the most straightforward method to 
construct atomistic resolution structures to interpret NMR experiments, but
enormous amount of simulation work was required for this work. The only practical
solution to collect these data was the open collaboration concept.
As result, we have produced original chemical insight for the atomistic resolution 
structures of phospholipids in various biologically relevant conditions.
